Non-word repetition in Yélî Dnye

### 2021-10-18 manuscript.Rmd
read new stim input file for nwr.by.freq.ITEM fig

```{r fig-xling-freq, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="NWR scores for individual target words as a function of the average frequency with which each phone is found across languages."}
aggregate(trnsc.inc$correct*100,by=list(trnsc.inc$target,trnsc.inc$avg_fr),mean)->xling
colnames(xling)<-c("Target","Avg_fr","Word")
stims.ipa <- read.xlsx("stimuli.xlsx") %>%
  select(target, target_ortho, phono)
xling <- merge(xling, stims.ipa, by.x = "Target", by.y = "target")

>>>>

```{r fig-xling-freq, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="NWR scores for individual target words as a function of the average frequency with which each phone is found across languages."}
aggregate(trnsc.inc$correct*100,by=list(trnsc.inc$target,trnsc.inc$avg_fr),mean)->xling
colnames(xling)<-c("Target","Avg_fr","Word")
stims.ipa <- read.xlsx("stimuli-20211018.xlsx") %>%
  select(target, target_ortho, phono)
xling <- merge(xling, stims.ipa, by.x = "Target", by.y = "target")
